混合效应模型和计量面板数据模型的区别

### 2019-03-24 Panel-and-Mixed-Model.Rmd
修改路径为/

## 混合模型

@@

```{r eval=T,echo=F,results='markup', cache=F}
library(plm)
data<-read.csv(".\\data\\pdataquality.csv")
data<-data[which(data$province!="全国"),]
#head(data)
## 将数据转化为面板数据
pdata<-pdata.frame(data,index=c("province","year"),drop.index=TRUE,row.names=TRUE)
#head(pdata)
## 建立混合模型
pdata.me<-plm(gdp~capital+labor+edu,data=pdata,model="pooling")
knitr::kable(summary(pdata.me)$coefficients, row.names =T, align = "c", caption="面板数据混合模型",
      digits=7,
      longtable = TRUE, booktabs = TRUE, linesep  = "")
```

@@

```{r eval=T,ecol=F}
library(lme4)
data<-read.csv(".\\data\\pdataquality.csv")
data<-data[which(data$province!="全国"),]
me.nlme<-lmer(gdp~capital+labor+edu+(1|province)+(capital|province)+(edu|province),data=data,REML=TRUE)
summary(me.nlme)
```

>>>>

## 混合模型(mixed model)

@@

```{r eval=T,echo=F,results='markup', cache=F}
library(plm)
data<-read.csv("./data/pdataquality.csv")
data<-data[which(data$province!="全国"),]
#head(data)
## 将数据转化为面板数据
pdata<-pdata.frame(data,index=c("province","year"),drop.index=TRUE,row.names=TRUE)
#head(pdata)
## 建立混合模型
pdata.me<-plm(gdp~capital+labor+edu,data=pdata,model="pooling")
knitr::kable(summary(pdata.me)$coefficients, row.names =T, align = "c", caption="面板数据混合模型",
      digits=7,
      longtable = TRUE, booktabs = TRUE, linesep  = "")
```

@@

```{r eval=T,ecol=F}
library(lme4)
data<-read.csv("./data/pdataquality.csv")
data<-data[which(data$province!="全国"),]
me.nlme<-lmer(gdp~capital+labor+edu+(1|province)+(capital|province)+(edu|province),data=data,REML=TRUE)
summary(me.nlme)
```
